{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-31 Paper/main.tex
fpcr theory

	\begin{equation}
		\begin{split}
			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right] \right]+ \epsilon(\omega) \\
		\end{split}
	\end{equation}

>>>>

	\begin{equation}
		\begin{split}
			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon(\omega)
			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}Z^{m,L}}+ \epsilon(\omega)
		\end{split}
	\end{equation}
